\tool: Revisiting BadUSB with Type-C

### 2021-01-29 WOOT/Files/experiment.tex
[experiment] restore figures
[experiment] volunteers amount

For an example, Brick\fengwei{reference?} is such a power bank sharing service
provider from Sweden. It provides power bank rental service all over the Sweden
and is planning on expanding their service around Europe. Moreover, this
service is even more popular in Asia, power bank stations are deployed in
markets, stores, and even newsstands.
%This suggests that this service is becoming more and more common around the global, especially in Asia and Europe.
\shuqing{I think we should paraphrase instead of using the descriptions on the website directly. Just to explain \textbf{what we need}.}

\fengwei{Explain the figure in the text.}
\begin{figure}[t]
	\centering
	\includegraphics[width=.4 \linewidth]{./Figs/Brick_station.png}
	\includegraphics[width=.4 \linewidth]{./Figs/jiedian.jpg}
	\caption{Two power banks station products}\shuqing{Photos that we took.}
	\label{fig:PBS_products}
\end{figure}

@@

\textbf{QR Code Payment}.
QR code payment is a new type of payment method that are popular in Asia. Its most well known cases are WeChat Pay and Alipay\fengwei{reference?}. QR code payment provides merchant and client a convenient way of offline payment while ensuring equivalent security as the credit card.
QR code payment is typically performed in the following steps:
\ding{182} The client presents payment QR code on mobile device to the merchant.
The QR code is encoded with a globally unique ID to identify the client's account.
\ding{183} The merchant scans the payment QR code and charges corresponding amount of money.
By presenting this QR code, the client authorizes proceeding charge.
\ding{184} An transaction generated by this scan is sent to the payment service provider.
Then the payment service provider requests the client to confirm the transaction.
\ding{185} After confirmation, the payment service provider proceed with this transaction and return the payment result to both the merchant and the client.
\shuqing{I think this paragraph can be shorter. No need to explain so many details.}
\hongyi{Dont know how to be more concise.}

@@

In the real-world scenario, some payment service providers use special rules
for micropayment purchases.  A micropayment is pre-determined by the payment
service provider with thresholds in the user agreement.  For example, WeChat
Pay~\cite{Wechat-pay} regards transaction under USD \textdollar 154 as
micropayments.  Different from a typical payment procedure, when micropayments
are made, confirmations can be applied automatically without clients'
permission which aims to provide convenience to both merchant and client.  If a
victim's payment code is leaked to the attackers, they can use the that code to
authorize multiple micropayments without permission.  In order to prevent such
cases, both Alipay and WeChat Pay has designed a refreshing mechanism for the
payment code, which is to refresh the QR code every minute. This is sufficient
to stop attack like sneak shots, but unable to stop real-time attack like our
\tool.  In summary, the payment QR code is highly sensitive on users' devices
and our following case study is about how to obtain this code using an
attacker-crafted power bank via \tool.

@@

\shuqing{Background is longer than real user study.}
As the functionality and effectiveness of scripting mode and remote control mode is rather clear, the former works similar to original BadUSB, the latter hijacks the victim's device completely.\hongyi{I dont know if it's a good enough reason}
Here we only validate the usability of privacy extraction mode and conducted a user study.
\shuqing{10 volunteers.}
We invited 6 volunteers to participate, who are unconscious of \tool details.
Before the experiment, we disclose to the volunteers about how their data might be used and request permission from both the volunteers and the institutional ethics review boards.
During the experiment, volunteers took turns to use their phones for half an hour with \tool connected, which are considered as a normal power bank.
In order to obtain data close to real life, they are requested to use phones just like when they use the shared power bank outside.
After the experiment, we introduced to them about our attack, analyze the screen recordings together to make sure their personal data is not at risk.
\shuqing{Do we need to mention that agreement the conference required here?}
\hongyi{I'm also quite concern about this.}

\subsubsection{Result}
After collecting the videos, we analyzed the video both automatically and manually.
During the automatic analysis, we used scripts to perform OCR recognition for each frame in the recorded video and stored all of the OCR results in a database.
At last, there are 38329 pieces of data collected among 6 volunteers.
\shuqing{The data may need to be updated.}
With these results, we could learn what content the victim was browsing.
Additionally, some keywords such as \textit{account, username and password} often appear with users' input data because they are often used as labels of input boxes.
Such keywords are more likely to lead us to user-specific data.
For example, when we searched with \textit{account} as keyword, victim's accounts can be found in the database, as shown in the Table~\ref{tab:ocr_keyword_example}.
\shuqing{Statistics.}
The frame number is the position of this frame in the recorded video, which indicates a target for manual analysis for further data extraction.

\begin{table*}[t]
	\centering
	\begin{tabular}{|l|l|l|l|}
		\hline
		Keyword  & Text                                                                                                                          & Name                           & Frame Number \\ \hline
		username & X 8B cas.******.edu.cn Username: 117***18 Password:                                                                           & \textless{}user1\textgreater{} & 385          \\ \hline
		username & Login Weibo Login with SMS and verification code ...... +86 151****4587 & \textless{}user5\textgreater{} & 1947         \\ \hline
		username & QQ 14*****50| Login with phone number New user registration 2345678 9 0                                                       & \textless{}user3\textgreater{} & 4308         \\ \hline
		username & connect to *** username h*****l Save account information Open VPN.....                                                        & \textless{}user6\textgreater{} & 7925         \\ \hline
		+86      & Login with phone number ...... +86 186****2483 |                                                                              & \textless{}user1\textgreater{} & 313          \\ \hline
	\end{tabular}
	\caption{Example of searching OCR results with some keywords}
	\label{tab:ocr_keyword_example}
\end{table*}

>>>>

For an example, Brick~\cite{Brick} is such a power bank sharing service
provider from Sweden. It provides power bank rental service all over the Sweden
and is planning on expanding their service around Europe. Moreover, this
service is even more popular in Asia, power bank stations are deployed in
markets, stores, and even newsstands.
%This suggests that this service is becoming more and more common around the global, especially in Asia and Europe.
\shuqing{I think we should paraphrase instead of using the descriptions on the website directly. Just to explain \textbf{what we need}.}

\fengwei{Explain the figure in the text.}
\begin{figure}[t]
	\centering
	\includegraphics[width=.45 \linewidth, height=.45 \linewidth]{./Figs/PBS_mt.png}
	\includegraphics[width=.45 \linewidth, height=.45 \linewidth]{./Figs/PBS_xd.png}
	\caption{Two power banks station products}
	\label{fig:PBS_products}
\end{figure}

@@

\textbf{QR Code Payment}.
QR code payment is a new type of payment method that are popular in Asia. Its most well known cases are WeChat Pay~\cite{Wechat-pay} and Alipay~\cite{AliPay}. QR code payment provides merchant and client a convenient way of offline payment while ensuring equivalent security as the credit card.
QR code payment is typically performed in the following steps:
\ding{182} The client presents payment QR code on mobile device to the merchant.
The QR code is encoded with a globally unique ID to identify the client's account.
\ding{183} The merchant scans the payment QR code and charges corresponding amount of money.
By presenting this QR code, the client authorizes proceeding charge.
\ding{184} An transaction generated by this scan is sent to the payment service provider.
Then the payment service provider requests the client to confirm the transaction.
\ding{185} After confirmation, the payment service provider proceed with this transaction and return the payment result to both the merchant and the client.
\shuqing{I think this paragraph can be shorter. No need to explain so many details.}
\hongyi{Dont know how to be more concise.}

@@

In the real-world scenario, some payment service providers use special rules
for micropayment purchases.  A micropayment is pre-determined by the payment
service provider with thresholds in the user agreement.  For example, WeChat
Pay~\cite{Wechat-pay} regards transaction under USD \textdollar 154 as
micropayments.  Different from a typical payment procedure, when micropayments
are made, confirmations can be applied automatically without clients'
permission which aims to provide convenience to both merchant and client.  If a
victim's payment code is leaked to the attackers, they can use the that code to
authorize multiple micropayments without permission.  In order to prevent such
cases, both WeChat Pay~\cite{Wechat-pay} and Alipay~\cite{AliPay} has designed a refreshing mechanism for the
payment code, which is to refresh the QR code every minute. This is sufficient
to stop attack like sneak shots, but unable to stop real-time attack like our
\tool.  In summary, the payment QR code is highly sensitive on users' devices
and our following case study is about how to obtain this code using an
attacker-crafted power bank via \tool.

@@

\shuqing{Background is longer than real user study.}
As the functionality and effectiveness of scripting mode and remote control mode is rather clear, the former works similar to original BadUSB, the latter hijacks the victim's device completely.\hongyi{I dont know if it's a good enough reason}
Here we only validate the usability of privacy extraction mode and conducted a user study.
\shuqing{10 volunteers.}
We invited 10 volunteers to participate, who are unconscious of \tool details.
Before the experiment, we disclose to the volunteers about how their data might be used and request permission from both the volunteers and the institutional ethics review boards.
During the experiment, volunteers took turns to use their phones for half an hour with \tool connected, which are considered as a normal power bank.
In order to obtain data close to real life, they are requested to use phones just like when they use the shared power bank outside.
After the experiment, we introduced to them about our attack, analyze the screen recordings together to make sure their personal data is not at risk.
\shuqing{Do we need to mention that agreement the conference required here?}
\hongyi{I'm also quite concern about this.}

\subsubsection{Result}
After collecting the videos, we analyzed the video both automatically and manually.
During the automatic analysis, we used scripts to perform OCR recognition for each frame in the recorded video and stored all of the OCR results in a database.
At last, there are 63882 pieces of data collected among 10 volunteers.
\shuqing{The data may need to be updated.}
With these results, we could learn what content the victim was browsing.
Additionally, some keywords such as \textit{account, username and password} often appear with users' input data because they are often used as labels of input boxes.
Such keywords are more likely to lead us to user-specific data.
For example, when we searched with \textit{account} as keyword, victim's accounts can be found in the database, as shown in the Table~\ref{tab:ocr_keyword_example}.
\shuqing{Statistics.}
The frame number is the position of this frame in the recorded video, which indicates a target for manual analysis for further data extraction.

\begin{table*}[t]
	\centering
	\begin{tabular}{|l|l|l|l|}
		\hline
		Keyword  & Text                                                                                                                          & Name                           & Frame Number \\ \hline
		username & X 8B cas.******.edu.cn Username: 11****18 Password:                                                                           & \textless{}user1\textgreater{} & 385          \\ \hline
		username & Login Weibo Login with SMS and verification code ...... +86 151****4587 & \textless{}user5\textgreater{} & 1947         \\ \hline
		username & QQ 14*****50| Login with phone number New user registration 2345678 9 0                                                       & \textless{}user3\textgreater{} & 4308         \\ \hline
		username & connect to *** username h*****l Save account information Open VPN.....                                                        & \textless{}user6\textgreater{} & 7925         \\ \hline
		+86      & Login with phone number ...... +86 186****2483 |                                                                              & \textless{}user1\textgreater{} & 313          \\ \hline
	\end{tabular}
	\caption{Example of searching OCR results with some keywords}
	\label{tab:ocr_keyword_example}
\end{table*}
